\documentclass[12pt]{article}
\begin{document}
\section{}
\newpage
\subsection{SCOPE:ERR - \textit{longin}}
\subsubsection{Brief}
This is a brief description of how SCOPE\_ ERR works. \\
\subsubsection{Description}
This detects the scope error.
\subsubsection{Bug Notes}
There are no reported bugs. I mean come on. There has to be a bug somewhere! I think I like to watch the stars. 

\subsubsection{Fields}
DTYP: stream\\\\ \textit{Because we have to use StreamDevice, we are required to put "stream" as the value of the DYTP field.}\\\\ 
FLNK: SCOPE:ERRMSG\\\\ INP: hp3458a.proto err 5700\\\\ TPRO: 1\\\\ \newpage
\subsection{SCOPE:RUN - \textit{bo}}
\subsubsection{Brief}
This is a brief description of how SCOPE\_ RUN works 
\subsubsection{Description}
I think zebras are really cute.
\subsubsection{Bug Notes}
Heck 

\subsubsection{Fields}
FLNK: SCOPE:RUNx\\\\ ONAM: Sample\\\\ TPRO: 1\\\\ ZNAM: Pause\\\\ \newpage
\subsection{SCOPE:RUNx - \textit{fanout}}
\subsubsection{Brief}
This is a brief description of how SCOPE\_ CR works. Shouldn't see this. \\
\subsubsection{Description}
This detects the scope error. Shouldn't see this.
\subsubsection{Bug Notes}
There are no reported bugs. I mean come on. There has to be a bug somewhere! I think I like to watch the stars. Shouldn't see this. 

\subsubsection{Fields}
LNK1: SCOPE:DISx\\\\ LNK2: SCOPE:RUN\\\\ TPRO: 1\\\\ \newpage
\subsection{SCOPE:ENAx - \textit{bo}}
\subsubsection{Fields}
DISV: 0\\\\ DTYP: stream\\\\ FLNK: SCOPE:I\\\\ OUT: hp3458a.proto setup 5600\\\\ SDIS: SCOPE:RUN\\\\ TPRO: 1\\\\ \newpage
\subsection{SCOPE:DISx - \textit{bo}}
\subsubsection{Fields}
DISV: 1\\\\ DTYP: stream\\\\ OUT: hp3458a.proto detach 5600\\\\ \textit{Try this out}\\\\ 
SDIS: SCOPE:RUN\\\\ TPRO: 1\\\\ \newpage
\subsection{SCOPE:I - \textit{ai}}
\subsubsection{Fields}
DISV: 0\\\\ DTYP: stream\\\\ EGU: A\\\\ FLNK: SCOPE:CNT\\\\ \textit{But this will}\\\\ 
INP: hp3458a.proto sample 5600\\\\ PREC: 9\\\\ SDIS: SCOPE:RUN NPP\\\\ TPRO: 1\\\\ \newpage
\subsection{SCOPE:RATE - \textit{calc}}
\subsubsection{Fields}
CALC: C:=A-B;B:=A;C\slash 10\\\\ DESC: Update rate\\\\ EGU: Hz\\\\ INPA: SCOPE:CNT NPP\\\\ PREC: 1\\\\ SCAN: 10 second\\\\ \end{document}
